Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
incooporated most of AP's comments

\author{T. K. Daisy Leung\altaffilmark{1, 2}}
\author{Andrea Pallottini\altaffilmark{3, 4}}
\author{Andrea Ferrara\altaffilmark{4, 5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7, 8}}

\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; }
\email{tleung@astro.cornell.edu}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (IPMU), The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
\altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify MCs and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC found in the arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}\approx$2 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

While ALMA has enabled the detections of
ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in
normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Smit18a},
we are still far from mapping their molecular ISM due to the cosmological dimming.
As such, we have undertaken a study, exploiting
state-of-the-art cosmological zoom-in hydrodynamic simulation
\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine
the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$) 
galaxy.

@@

\subsection{\ncode{Serra} Simulation\footnote{Serra means greenhouse in Italian which is motivated by the
fact that our simulation includes a chemical network to calculate the abundance of H$_2$, which in turn
dictates the formation of CO.
}}
The simulation used in this work is described by \citealt{Pallottini17a} and is briefly summarized here.

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high baryonic density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
%\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
% (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

\subsection{Star Formation History} \label{sec:sfh}
One of the advantage of studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures compared to more evolved galaxies found at 
a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
ones). % mainly expecting differences in alpha_vir, sigma, M_cl.

@@

\subsection{Structure identification} \label{sec:method}
To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (aka k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. 
In the customized version used for this study, we modify the function to enhance the stability of the code (which essentially means we fixed the bugs in order for it to actually work).

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.png}
  \\[-5.5em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.png}
  \\[-5.5em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.png}
\caption{
MC identified by applying
volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
	Color shows the projected H$_2$ surface density. {\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field; additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear... hmm.. Not worth my time to fix this for the report.}
% yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see Appendix of \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

The mass of an MC is calculated from the uniformly-gridded 3D density field,
integrating over all zones of the MC, multiplied by its volume. 
The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
the one-dimensional non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{xyz} \sum_{i}^N \rho_i \left(\mathbf{v} - \mathbf{\bar v}\right)_{xyz}^2}{\sum_i^N \rho_i},
\end{equation}
where $N$ is the number of zones of each MC.
The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities\footnote{We find comparable velocity dispersion between that derived from 
taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that
rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion ($\sigma$).}.

We show in \Fig{dist} the MC distributions in terms of their
molecular gas masses, radii, and gas mass fractions, which we define as 
\begin{equation}
f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass.
We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified.
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

@@

\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:alpha}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation), 
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities (see bottom panels of \Fig{alpha16} and 
\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

@@

\subsection{Single Snapshots}  \label{sec:singless}

>>>>

\author{T. K. Daisy Leung\altaffilmark{1, 2}}
\author{Andrea Pallottini\altaffilmark{3, 4}}
\author{Andrea Ferrara\altaffilmark{4, 5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7
%mm, 8   [I only use the Drexel affiliation when working with folks
%from there...]
}}

\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; }
\email{tleung@astro.cornell.edu}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (IPMU), The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
%mm \altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify MCs and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC found in the arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}\approx$2 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

While ALMA has enabled the detections of
ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission inr
normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Odorico18a, Carniani18b},
we are still far from mapping their molecular ISM due to the cosmological dimming.
As such, we have undertaken a study, exploiting
state-of-the-art cosmological zoom-in hydrodynamic simulation
\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine
the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$) 
galaxy.

@@

\subsection{\ncode{Serra} Simulation\footnote{Serra means greenhouse in Italian which is motivated by the
fact that our simulation includes a chemical network to calculate the abundance of H$_2$, which in turn
dictates the formation of CO.
}}
The simulation used in this work is described by \citealt{Pallottini17a, Pallottini17b} and is briefly summarized here.

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
%\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
% (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

\subsection{Star Formation History} \label{sec:sfh}
One of the advantage of studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
% {\AP potentially moving the following, maybe postpone after structures have been identified as a description? }
% {\DL or maybe in the discussion section?}
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures compared to more evolved galaxies found at 
a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
ones). % mainly expecting differences in alpha_vir, sigma, M_cl.

@@

\subsection{Structure identification} \label{sec:method}
To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. 
In the customized version used for this study, we modify the function to enhance the stability of the code.
% (which essentially means we fixed the bugs in order for it to actually work).

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.png}
  \\[-5.5em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.png}
  \\[-5.5em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.png}
\caption{
Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is only a subset of all the $n_{\rm cut}$ adopted (see text).
	Color shows the H$_2$ surface density, weighted by the column density. Specifically, this is calculated using \Eq{integrate}.
	\AP{additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear... hmm.. Not worth my time to fix this for the report.}
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions within $R\sim$3.5\,kpc from the galaxy center\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of
$\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.

In \Fig{MC}, we over-plotted the molecular structures identified using
a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps as an example.
The plots shown in \Fig{MC} are weighted by the total gas density; that is, 
\begin{equation}
{\rm pixel} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
\label{eqn:integrate}
\end{equation} 
where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.

Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

The mass of an MC is calculated from the uniformly-gridded 3D density field,
integrating over all zones of the MC, multiplied by its volume. 
The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
% {\AP The size is an effective radius, calculated from the total volume of the MC assuming spherical symmetry.}
Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
the non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
which is summed over the cells composing each MC.
The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities\footnote{We find comparable velocity dispersion between that derived from 
taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that
rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion ($\sigma$).}.
This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MC distributions in terms of their
molecular gas masses, radii, and gas mass fractions, which we define as 
\begin{equation}
f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass.
We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified. 
% {\AP  maybe we can tie it to the mass resolution limitation imposed by our criterion.}
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

@@

\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
{\AP I fear that putting this subsection here breaks a bit the flow of the analysis of the results. Maybe we can put it as an appendix and keep only eq. 10 in the main text (a put it at when analysing the relevant plot)? }

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:alpha}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation), 
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities (see bottom panels of \Fig{alpha16} and 
\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

@@

\subsection{MC Properties}
\subsubsection{Single Snapshots}  \label{sec:singless}
